Single-step Hybrid Predition

### 2016-11-22 reports/loocv_reduced.Rmd
Remove conclusions from reports

## Predictive Abilities
```{r Coefficient-of-Variation-Plot, cache = TRUE, fig.cap = "Coefficient of variation for seven agronomic traits and nine sets of predictors."}
overview_df %>%
  filter(Predictor != "snp77-none-none") %>%
  mutate(Predictor = fct_relevel(Predictor, pred_order)) %>%
  ggplot(aes(x = CV, y = Predictor)) +
  geom_segment(aes(yend = Predictor), xend = 0, color = "gray50") +
  geom_point(aes(color = Predictor), size = 3) +
  scale_color_viridis(discrete = TRUE, option = "inferno") +
  facet_wrap(~ Trait, scales = "free_x") +
  theme_bw() +
  theme(panel.grid.major.y = element_blank(),
        axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1),
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        legend.position = c(0.7, 0.13)
  ) +
  guides(color = guide_legend(ncol = 2,
                              reverse = FALSE)) +
  xlab("Coefficient of Variation") +
  ylab("Predictor Set") +
  xlim(0, NA)
```

Plot the predictive abilities for all predictor-trait combinations 
separately for the reduced and the full data set, respectively.
```{r Predictive-Ability-Plots, cache = TRUE, fig.height = 10, fig.cap = "Predictive ability for seven agronomic traits (rows) and nine predictor sets (columns). The predictor sets are split into the categories 'Reduced' (i.e. 685 hybrids) and 'Full' (i.e. 1,521 hybrids)."}
overview_df %>%
  as_tibble() %>%
  filter(Predictor != "snp77-none-none") %>%
  mutate(Predictor = fct_relevel(Predictor, pred_order),
         Group = fct_relevel(Group, "Reduced", "Full")
  ) %>%
  ggplot(aes(x = Predictor, y = r)) +
  geom_bar(stat = "identity", aes(fill = Predictor), color = "black") +
  geom_text(aes(label = round(r, digits = 3)), vjust = -0.2) +
  scale_fill_viridis(discrete = TRUE, option = "inferno") +
  facet_grid(Trait ~ Group, space = "free", scales = "free_x") +
  theme_bw() +
  theme(
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank(),
    axis.title.x = element_blank(),
    legend.position = "bottom",
    legend.key = element_rect(color = "white")
  ) +
  guides(fill = guide_legend(nrow = 3,
                             byrow = TRUE,
                             keywidth = 0.25,
                             keyheight = 0.25,
                             default.unit = "inch",
                             title.position = "top")
  ) +
  ylim(c(0, 1))
```

>>>>

```{r Coefficient-of-Variation-Plot, cache = TRUE, fig.cap = "Coefficient of variation for seven agronomic traits and nine sets of predictors."}
overview_df %>%
  filter(Predictor != "snp77-none-none") %>%
  mutate(Predictor = fct_relevel(Predictor, pred_order)) %>%
  ggplot(aes(x = CV, y = Predictor)) +
  geom_segment(aes(yend = Predictor), xend = 0, color = "gray50") +
  geom_point(aes(color = Predictor), size = 3) +
  scale_color_viridis(discrete = TRUE, option = "inferno") +
  facet_wrap(~ Trait, scales = "free_x") +
  theme_bw() +
  theme(panel.grid.major.y = element_blank(),
        axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1),
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        legend.position = c(0.7, 0.13)
  ) +
  guides(color = guide_legend(ncol = 2,
                              reverse = FALSE)) +
  xlab("Coefficient of Variation") +
  ylab("Predictor Set") +
  xlim(0, NA)
```

## Predictive Abilities
```{r Predictive-Ability-Plots, cache = TRUE, fig.height = 10, fig.cap = "Predictive ability for seven agronomic traits (rows) and nine predictor sets (columns). The predictor sets are split into the categories 'Reduced' (i.e. 685 hybrids) and 'Full' (i.e. 1,521 hybrids)."}
overview_df %>%
  as_tibble() %>%
  filter(Predictor != "snp77-none-none") %>%
  mutate(Predictor = fct_relevel(Predictor, pred_order),
         Group = fct_relevel(Group, "Reduced", "Full")
  ) %>%
  ggplot(aes(x = Predictor, y = r)) +
  geom_bar(stat = "identity", aes(fill = Predictor), color = "black") +
  geom_text(aes(label = round(r, digits = 3)), vjust = -0.2) +
  scale_fill_viridis(discrete = TRUE, option = "inferno") +
  facet_grid(Trait ~ Group, space = "free", scales = "free_x") +
  theme_bw() +
  theme(
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank(),
    axis.title.x = element_blank(),
    legend.position = "bottom",
    legend.key = element_rect(color = "white")
  ) +
  guides(fill = guide_legend(nrow = 3,
                             byrow = TRUE,
                             keywidth = 0.25,
                             keyheight = 0.25,
                             default.unit = "inch",
                             title.position = "top")
  ) +
  ylim(c(0, 1))
```
